Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2023-07-14 Manuscript.Rmd
updated intro

affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University"
date: "`r Sys.Date()`"
output:
  word_document:
  html_document: default
  pdf_document:
    latex_engine: xelatex
bibliography: knitting files/Citations.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
  - id : "3"
    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
  - id : "4"
    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
  - id : "4"
    institution : "Danish Pain Research Center, Aarhus University, Denmark"
date: "`r Sys.Date()`"
output:
  word_document:
  html_document: default
  pdf_document:
    latex_engine: xelatex
bibliography: knitting files/Citations.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---
